\begin{rSection}{Conference Proceedings}
	\begin{timeline}
		2021
			& \textbf{White, M. C. A.}, Ben-Zion, Y., \& Vernon, F. L. (2021, 08). A Detailed Earthquake Catalog for the San Jacinto Fault‐Zone Region in Southern California and the period 2008-2020. Poster Presentation at 2021 SCEC Annual Meeting.
			\\
			\\
			& \textbf{White, M. C. A.}, Ben-Zion, Y., \& Vernon, F. (2021). Catalog Update: A Detailed Earthquake Catalog for the San Jacinto Fault Zone Region in Southern California.  \textit{Seismological Research Letters, 92}(2B), p. 1430. doi: 10.1785/0220210025
			\\
			\\
		2020 
			& \textbf{White, M. C. A.}, Fang, H., Catchings, R. D., Goldman, M. R., Steidl, J. H., \& Ben-Zion, Y. (2020). Detailed traveltime tomography and seismicity around the 2019 M7.1 Ridgecrest, CA, earthquake using dense rapid-response seismic data. S070-08 presented at 2020 Fall Meeting, AGU, San Francisco, CA, 1-17 December.
			\\
			\\
			& Fang, H., \textbf{White, M. C. A.}, Lu, Y., van der Hilst, R. D., \& Ben-Zion, Y. (2020). Regional seismic velocity models for Southern California based on travel time tomography with Poisson Voronoi cells parameterization.  S070-04 presented at 2020 Fall Meeting, AGU, San Francisco, CA, 1-17 December.
			\\
			\\
			& Luckie, T., Gase, A., Jacobs, K., \textbf{White, M. C. A.}, Henrys, S. A., Okaya, D. A., Van Avendonk, H. J., Bangs, N. L., Barker, D. H. N., Bassett, D., Kodaira, S., Arai, R., Fujie, G., \& Yamamoto, Y. (2020). P-wave velocity structure of the northern Hikurangi margin from travel time tomography. T017-0010 presented at 2020 Fall Meeting, AGU, San Francisco, CA, 1-17 December.
			\\
			\\
			& \textbf{White, M. C. A.}, Fang, H., Catchings, R. D., Goldman, M. R., Steidl, J. H., \& Ben-Zion, Y. (2020). Detailed traveltime tomography and seismicity around the 2019 M7.1 Ridgecrest, CA, earthquake using dense rapid-response seismic data. Poster Presentation at 2020 SCEC Annual Meeting.
			\\
			\\
			& Catchings, R. D., Goldman, M. R., \textbf{White, M. C. A.}, Qiu, H., \& Ben-Zion, Y. (2020). Results from dense nodal-array recordings of the 2019 Ridgecrest Sequence aftershocks. Oral Presentation at 2020 SCEC Annual Meeting.
			\\
			\\
		2019
			& \textbf{White, M. C. A.}, Fang, H., van der Hilst, R. D., \& Ben-Zion, Y. (2019). The distribution of microseismicity correlates closely with velocity structure in the San Jacinto fault-zone region of Southern California. S21C-07 presented at 2019 Fall Meeting, AGU, San Fransisco, CA, 9-13 December.
			\\
			\\
			& Nakata, N., Fang, H., \textbf{White, M. C. A.}, \& Pitarka, A. (2019). Shallow crustal heterogeneity in Southern California estimated from earthquake coda waves. Poster Presentation at 2019 SCEC Annual Meeting.
			\\
			\\
			& \textbf{White, M. C. A.}, Ben-Zion, Y., \& Vernon, F. L. (2019). Focal Mechanisms of Microseismicity in the San Jacinto Fault Zone Region of
			Southern California. \textit{Seismological Research Letters, 90}(2B), p. 1042. doi: 10.1785/0220190061
			\\
			\\
		2018
			& \textbf{White, M. C. A.}, Ben-Zion, Y., \& Vernon, F. L. (2018). Detailed seismic catalog for the San Jacinto fault zone region (2008-2016) from automated processing of raw waveform data. Poster Presentation at 2018 SCEC Annual Meeting.
			\\
			\\
		2017
			& \textbf{White, M. C. A.}, Ross, Z. E., Vernon, F. L., \& Ben-Zion, Y. (2017). A Detailed Automatic Seismicity Catalog (1998-2015) for the San Jacinto Fault Zone Region. \textit{Seismological Research Letters, 88}(2B), p. 569. doi: 10.1785/0220170035
			\\
			\\
			& \textbf{White, M. C. A.}, Ross, Z. E., Ben-Zion, Y., \& Vernon, F. L. (2017). A detailed, automatically-derived, seismicity catalog for the San Jacinto fault zone (1998-2016). Poster Presentation at 2017 SCEC Annual Meeting.
			\\
			\\
		2016
			& \textbf{White, M. C. A.}, Ross, Z. E., Vernon, F. L., \& Ben-Zion, Y. (2016). A detailed automatic 1998-2015 earthquake catalog of the San Jacinto fault zone region. Poster Presentation at 2016 SCEC Annual Meeting.
			\\
			\\
		2015
			& \textbf{White, M. C. A.}, Ross, Z. E., Vernon, F. L., \& Ben-Zion, Y. (2015). A Large Scale Automatic Earthquake Location Catalog in the San Jacinto Fault Zone Area Using An Improved Shear-Wave Detection Algorithm. S11A-2775 presented at 2015 Fall Meeting, AGU, San Francisco, CA, 14-18 December.
			\\
			\\
			& \textbf{White, M. C. A.}, Ross, Z. E., Reyes, J. C., Vernon, F. L., \& Ben-Zion, Y. (2015). An Improved Algorithm for Automatic Picking of Seismic S-wave Arrivals in Continuous Data with Application to the San Jacinto Fault Zone. \textit{Seismological Research Letters, 86}(2B), p. 731. doi: 10.1785/0220150017
			\\
			\\
			& Ben-Zion, Y., Vernon, F. L., Ozakin, Y., Zigone, D., Ross, Z., Meng, H., \textbf{White, M. C. A.}, Reyes, J. C., Hollis, D., \& Barklage, M. (2015). Basic Wave Propagation Results from a Highly-Dense Seismic Array on the San Jacinto Fault Zone. \textit{Seismological Research Letters, 86}(2B), p. 594. doi: 10.1785/0220150017
			\\
			\\
		2014 
			& Vernon, F. L., Reyes, J. C., \textbf{White, M. C. A.}, Davis, G. A., Meyer, J. C., Sahakian, V. J., Mancinelli, N. J., Ben-Zion, Y., Zigone, D., Harris, C. W., Liu, X., Qiu, H., Share., P.-E., Ozakin, Y., Hollis, D., \& Barklage, M. (2014). Observations at a San Jacinto Fault Zone site (Sage Brush Flat) Using a Nodal Seismic High Frequency Array. T11F-08 presented at 2014 Fall Meeting, AGU, San Francisco, CA, 15-19 December.
			\\
			\\
			& Tytell, J. E., Cox, T. A., \textbf{White, M. C. A.}, Martynov, V. G., Eakins, J., \& Vernon, F. L. (2014). The ANF Catalog of Central United States Seismicity. S51A-4381 presented at 2014 Fall Meeting, AGU, San Francisco, CA, 15-19 December.
			\\
			\\
		2013
			& Mulder, T., Brillon, C., Bentkowski, W., \textbf{White, M. C. A.}, Rosenberger, A., Rogers, G. C., Vernon, F. L., \& Kao, H. (2013). Analysis of the 2012 Oct 27 Haida Gwaii Aftershock Sequence. S32A-08 presented at 2013 Fall Meeting, AGU, San Francisco, CA, 9-13 December.
			\\
			\\
		2011
			& Mulder, T., Brillon, C., Bentkowski, W., \textbf{White, M. C. A.}, Rosenberger, A., Rogers, G. C., Vernon, F. L., \& Kao, H. (2011). WaveHRL: a high resolution, modular seismic event system and its application to the L'Aquila 2009 earthquake sequence. S32A-08 presented at 2011 Fall Meeting, AGU, San Francisco, CA, 5-9 December.
	\end{timeline}
\end{rSection}