\begin{rSection}{Publications}
	\subsubsection*{Manuscripts Under Review}
	\begin{enumerate}
		\item \textbf{White, M.~C.~A.}, Sharma, K., Li, A., Kumar, T.~K.~S., \& Nakata, N. FastMapSVM: Classifying complex objects using the FastMap algorithm and Support-Vector Machines. \textit{Communications Engineering}
		
		\item \textbf{White, M.~C.~A.}, Zhang Z., Bai T., Qiu H., Chang H. \& Nakata N. HDF5eis: A Solution for Storage and Access to Big, Multidimensional Data from Environmental Sensors. \textit{GEOPHYSICS}
		
		\item Zhang, Z., \textbf{White, M.~C.~A.}, Bai, T., Qiu, H., \& Nakata, N. Characterizing Microseisms Induced by Hydraulic Fracturing with Hybrid Borehole DAS and Three-Component Geophone Data. \textit{GEOPHYSICS}
	\end{enumerate}
	\subsubsection*{Refereed Journal Articles}
		\begin{enumerate}
					
		\item Nakata N., Nakata R., Kato A., Xue Z., \& \textbf{White, M.~C.~A.} (In Press). Enigmatic doubly scattered tube waves at a crosswell seismic survey. \textit{Geophysical Journal International}
			
		\item Fang, H., \textbf{White, M.~C.~A}., Lu, Y., \& Ben-Zion, Y. (2022). Seismic traveltime tomography of Southern California using Poisson-Voronoi cells and 20 years of data. \textit{Journal of Geophysical Research: Solid Earth}. doi: 10.1029/2021JB023307
		
		%		\item \textbf{White, M. C. A.}, Ben-Zion, Y. \& Vernon, F. L. (In preparation). Catalog Update (2008-2020): A Detailed Earthquake Catalog for the San Jacinto Fault Zone Region in Southern California.
		
		\item Jiang, C., Zhang, P., \textbf{White, M.~C.~A.}, Pickle, R., \& Miller, M.~S. (2022). A Detailed Earthquake Catalog for Banda Arc–Australian Plate Collision Zone Using Machine-Learning Phase Picker and an Automated Workflow. \textit{The Seismic Record, 2}(1), 1–10. doi: 10.1785/0320210041
		
		\item \textbf{White, M. C. A.}, Fang, H., Catchings, R. D., Goldman, M. R., Steidl, J. H., \& Ben-Zion, Y. (2021). Detailed traveltime tomography and seismic catalogue around the 2019 M w7.1 Ridgecrest, California, earthquake using dense rapid-response seismic data. \textit{Geophysical Journal International, 227}(1), 204–227. doi: 10.1093/gji/ggab224
		
		\item \textbf{White, M. C. A.}, Fang, H., Nakata, N., \& Ben-Zion, Y. (2020). PyKonal: A Python package for solving the Eikonal equation in spherical and Cartesian coordinates using the Fast Marching Method. \textit{Seismological Research Letters,  91}(4), 2378-2389. doi: 10.1785/0220190318
		
		\item \textbf{White, M. C. A.}, Ben‐Zion, Y., \& Vernon, F. L. (2019). A Detailed Earthquake Catalog for the San Jacinto Fault‐Zone Region in Southern California. \textit{Journal of Geophysical Research: Solid Earth, 124}, 6908–6930. doi: 10.1029/2019JB017641
		
		\item Burdick, S., Vernon, F. L., Martynov, V., Eakins, J., Cox, T., Tytell, J., \dots van der Hilst, R. D. (2017). Model Update May 2016: Upper‐Mantle Heterogeneity beneath North America from Travel‐Time Tomography with Global and USArray Data. \textit{Seismological Research Letters, 88}(2A), 319–325. doi: 10.1785/0220160186
		
		\item Ross, Z. E., Ben-Zion, Y., \textbf{White, M. C.}, \& Vernon, F. L. (2016). Analysis of earthquake body wave spectra for potency and magnitude values: implications for magnitude scaling relations. \textit{Geophysical Journal International, 207}(2), 1158–1164. doi: 10.1093/gji/ggw327
		
		\item Ross, Z. E., \textbf{White, M. C.}, Vernon, F. L., \& Ben‐Zion, Y. (2016). An Improved Algorithm for Real‐Time S ‐Wave Picking with Application to the (Augmented) ANZA Network in Southern California. \textit{Bulletin of the Seismological Society of America, 106}(5), 2013–2022. doi: 10.1785/0120150230
		
		\item Ben-Zion, Y., Vernon, F. L., Ozakin, Y., Zigone, D., Ross, Z. E., Meng, H., \dots Barklage, M. (2015). Basic data features and results from a spatially dense seismic array on the San Jacinto fault zone. \textit{Geophysical Journal International, 202}(1), 370–380. doi: 10.1093/gji/ggv142
		
		\item Astiz, L., Eakins, J. A., Martynov, V. G., Cox, T. A., Tytell, J., Reyes, J. C., \dots Vernon, F. L. (2014). The Array Network Facility Seismic Bulletin: Products and an Unbiased View of United States Seismicity. \textit{Seismological Research Letters, 85}(3), 576–593. doi: 10.1785/0220130141
	\end{enumerate}
	\subsubsection*{Conference Proceedings}
		\begin{enumerate}
			\item \textbf{White, M. C. A.}, Nakata, N., Rodríguez Tribaldos, V., Nayak, A., \& Dobson, P. Seismotectonic Evolution and Geothermal Energy Production in the Salton Sea Geothermal Field (2023) 2023 Stanford Geothermal Workshop.
		
			\item Bai T., Zhang Z., \textbf{White, M.~C.~A.}, Qiu H., Williamson P., \& Nakata N. (2022) A ``sliding box'' automatic relocation method based on geometric-mean reverse-time migration, \textit{SEG Technical Program Expanded Abstracts}: 1516-1520.
			doi: 10.1190/image2022-3747339.1
		\end{enumerate}
\end{rSection}